%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Chandrashekhar Tripathi resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% formatting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{article}

\usepackage[hmargin=0.75cm, vmargin=0.8cm]{geometry}

\usepackage[hidelinks]{hyperref}  % links (href)

\usepackage{multicol}     % 2 columns
\setlength\columnsep{20pt}

% colors
% Color definitions
\usepackage[usenames,dvipsnames]{xcolor} 
\definecolor{date}{HTML}{666666}
\definecolor{primary}{HTML}{2b2b2b}
\definecolor{headingclr}{HTML}{6A6A6A}
\definecolor{subheadingclr}{HTML}{333333}
\definecolor{light}{HTML}{BBBBBB}

% fonts
\usepackage[]{fontspec}
\setmainfont[Color = primary, Path = fonts/OpenSans/OpenSans/, BoldItalicFont=OpenSans-MediumItalic, BoldFont=OpenSans-Medium, ItalicFont=OpenSans-MediumItalic]{OpenSans-Light}


% titles
%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{titlesec} % or RequirePackage[loadonly]{titlesec} in a cls file
\titleformat{\subsection}[runin]{
  \color{subheadingclr}
  \fontsize{13pt}{13pt}\bfseries\selectfont
}{}{0em}{}
\titleformat{\subsubsection}[runin]{\fontsize{10pt}{10pt}\selectfont}{}{0em}{}

\titleformat{\section}{
  \color{subheadingclr}
  \fontspec[Path = fonts/ZillaSlab/]{ZillaSlab-Light}\fontsize{16pt}{24pt}\selectfont \raggedright\uppercase
}{}{0em}{}

% spacing 
\titlespacing{\section}{0pt}{8pt}{4pt} 
\titlespacing{\subsection}{0pt}{8pt}{0pt}
\titlespacing{\subsubsection}{0pt}{4pt}{0pt}

% custom commands
\newcommand{\namesection}[3]{
  \begin{multicols}{2}
    \begin{flushleft}
      \fontsize{30pt}{25pt}
      \fontspec[Path = fonts/ZillaSlab/]{ZillaSlab-Light}
      {{ #1 }\\{ #2 }}
      \columnbreak\\
    \end{flushleft}
    \begin{flushright}
      { #3 }
    \end{flushright}
  \end{multicols}
  \vspace{-10pt}
}

\newcommand{\subheading}[2]{
  {\subsection{#1}
  \hfill{#2}}\\
  \vspace{2pt}
}

\newcommand{\subsubheading}[2]{
  {\subsubsection{#1}
  \hfill \small#2} \\
  \vspace{2pt}
}

\newcommand{\descript}[1]{
  {\color{subheadingclr}
  \raggedright\fontspec[Path = fonts/Raleway/]{Raleway-Medium}\fontsize{10pt}{12pt}\selectfont {\scshape#1} \normalfont}
}

\newcommand{\datelocation}[1]{
  {\color{date}\fontsize{10pt}{12pt}\bfseries { #1 } \normalfont\\}
}

% custom environments
\newenvironment{tightemize}{
\vspace{-8pt}\begin{itemize}\itemsep1pt \parskip0pt \parsep0pt}
{\end{itemize}\vspace{-\topsep}}

% Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\namesection{Chandrashekhar}{Tripathi}{+91 (844) 805-2150\\
  \href{mailto:tripathics17@gmail.com}{tripathics17@gmail.com}
  \par
  National Institute of Technology\\
  Arunachal Pradesh (IN)}

\centering{
  LinkedIn://\href{https://linkedin.com/in/tripathics}{\textbf{tripathics}} | 
  \href{https://tripathics.github.io}{tripathics.github.io} | 
  GitHub://\href{https://github.com/tripathics}{\textbf{tripathics} }
}
\noindent\makebox[\linewidth]{\color{light}\rule{\paperwidth}{0.2pt}}
\vspace{-15pt}

\begin{multicols}{2}
  \begin{flushleft}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    \section{Education}    
    \subsection{NIT Arunachal Pradesh}
    \subsubheading{B. Tech in Computer Science Eng}{Oct 2020-2024}
    Cum. GPA: \textbf{8.9 / 10 (Expected)}

    \subsection{Govt. Higher Sec. School, Rupa}
    \subsubheading{Higher Secondary, XII (CBSE)}{Grad. Mar 2019}
    Percentage: \textbf{81.6\%, 1\textsuperscript{st} in District}

    \subsubheading{Secondary, X (CBSE)}{Grad. Mar 2017}
    Cum. GPA: \textbf{10 / 10}
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % COURSEWORK
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    
    \section{Coursework}
    % \subheading{Undergraduate}{}
    \begin{tightemize}
      \item Data Structures \& Algorithms
      \item Object Oriented Programming
      \item Operating Systems
      \item Database Management Systems
      \item Machine Learning
      \item Unix Tools and Scripting
    \end{tightemize}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    
    \section{Experience}
    \subheading{Indian Oil Corp. Ltd}{\descript{SDE Intern}}
    \datelocation{Dec 2022 - Present | Assam, IN}

    \begin{tightemize}
      \item Interned as a full-stack and IoT developer, developing a client and admin-side application integrated with an IoT device.
      \item Achieved selection for the internship from among the top 3\% of students in college.
    \end{tightemize}

    \subheading{Technodaya}{\descript{Editor}}
    \datelocation{Sep 2022 - Present | NIT Arunachal Pradesh}
    \begin{tightemize}
      \item Collaborated with 2 teammates to develop Technodaya Newsletter website, cutting paperwork by 90\%.
      \item Utilized React for frontend and Firebase for backend as a full stack developer.
      \item Automated content generation, resulting in a 70\% reduction in editors' workload.
    \end{tightemize}

    \subheading{Ekarigari Solutions Pvt. Ltd}{\descript{IoT Intern}}
    {
      \color{date}\fontsize{10pt}{12pt}\bfseries
      Aug 2022 - Sep 2022 | Remote
    }
    \begin{tightemize}
      \item Worked with the Ekarigari team on a Smart Home Automation.
      \item Utilised NodeMCU and Arduino creating a system faster than 50\% of existing systems.
    \end{tightemize}

    \columnbreak

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    
    \section{Skills}
    \subheading{Technical}{}
    \begin{tightemize}
      \item \textbf{Languages:} C, C++, Java
      \item \textbf{Scripting languages:} Bash shell, Python
      \item \textbf{Frameworks:} React, Flask, Node
      \item \textbf{Database:} MongoDB, SQL
      \item \textbf{Platforms:} Linux, Firebase
      \item \textbf{Familiar:} Typescript, Docker, Android
      \item \textbf{Others:} git, Microsoft Office, Sketchup
    \end{tightemize}

    \subheading{Soft Skills}{}
    Leadership \textbullet{} Teamwork \textbullet{} Communication \textbullet{} Organization

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % PROJECTS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    \section{Projects}

    \subheading{Atulyam'23 website}{
      \href{https://atulyam23.com}{Website} | 
      \href{https://github.com/tripathics/atulyam-2023}{Source} 
    }
    \begin{tightemize}
      \item Developed NITAP's \textbf{Atulyam Fest} website, utilizing frontend design skills to create a magazine-style UI/UX.
      \item Implemented Firebase authentication and Firestore database to optimize user experience.
    \end{tightemize}

    \subheading{Airavat}{\href{https://github.com/tripathics/airavat}{Source}}
    \begin{tightemize}
      \item Created \textbf{Airavat}, an IoT ecosystem for fleet vehicle monitoring and tracking.
      \item Tracker device made using NodeMCU (ESP8266), 4G SIM Module (SIM7600) and GPS module (GPS NEO-7M).
      \item Developed full stack website for Airavat using Flask with SQL database.
    \end{tightemize}

    \subheading{Technodaya Website}{
      \href{https://technodaya.netlify.app}{Website} | 
      \href{https://github.com/PursottamSah6003}{Source}
    }
    \begin{tightemize}
      \item Created full stack website for \textbf{Technodaya}, technical newsletter of NIT Arunachal Pradesh.
      \item Full stack developer - React frontend and Firebase backend.
      \item Intuitive card layout to rearrange magaine sections. 
    \end{tightemize}

    \subheading{SHIELD web app}{\href{https://github.com/tripathics}{Source}}
    \begin{tightemize}
      \item Co-developed \textbf{SHIELD}, an IoT-based ecosystem for secure transportation of valuables with \textbf{Team Revolutionists}.
      \item Created a full-stack web app enabling shipment tracking, locking/unlocking, and warning alert monitoring for admins.
      \item Awarded \textbf{1\textsuperscript{st} place} in the NVCTI Winter Challenge Hackathon.
    \end{tightemize}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % ACHIEVEMENTS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    \section{Achievements}
    \begin{tabular}{rll}
      2022 & 1\textsuperscript{st} prize & NVCTI winter challenge Hackathon\\
      2022 & 1\textsuperscript{st} prize & NITAP Designathon 2022\\
      2022 & 1\textsuperscript{st} prize & Idea pitching, NIT Arunachal Pradesh\\
      2022 & 1\textsuperscript{st} prize & CSS battle, Addovedi 2022\\
    \end{tabular}
  \end{flushleft}
\end{multicols}

\end{document}