%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Chandrashekhar Tripathi resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% formatting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{article}

\usepackage[hmargin=0.8cm, vmargin=0.8cm]{geometry}

\usepackage[hidelinks]{hyperref}  % links (href)

\usepackage{multicol}     % 2 columns
\setlength\columnsep{1cm}

% colors
% Color definitions
\usepackage[usenames,dvipsnames]{xcolor} 
\definecolor{date}{HTML}{666666}
\definecolor{primary}{HTML}{2b2b2b}
\definecolor{headingclr}{HTML}{6A6A6A}
\definecolor{subheadingclr}{HTML}{333333}
\definecolor{light}{HTML}{BBBBBB}

% fonts
\usepackage[]{fontspec}
\setmainfont[Color = primary, Path = fonts/OpenSans/OpenSans/, BoldItalicFont=OpenSans-MediumItalic, BoldFont=OpenSans-Medium, ItalicFont=OpenSans-LightItalic]{OpenSans-Light}


% titles
%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{titlesec} % or RequirePackage[loadonly]{titlesec} in a cls file
\titleformat{\subsection}[runin]{
  \color{subheadingclr}
  \fontsize{12pt}{12pt}\bfseries\selectfont
}{}{0em}{}
\titleformat{\subsubsection}[runin]{\fontsize{9pt}{9pt}\selectfont}{}{0em}{}

\titleformat{\section}{
  \color{subheadingclr}
  \fontspec[Path = fonts/ZillaSlab/]{ZillaSlab-Light}\fontsize{16pt}{24pt}\selectfont \raggedright\uppercase
}{}{0em}{}

% spacing 
\titlespacing{\section}{0pt}{16pt}{8pt} 
\titlespacing{\subsection}{0pt}{12pt}{4pt}
\titlespacing{\subsubsection}{0pt}{4pt}{0pt}

% custom commands
\newcommand{\namesection}[3]{
  \begin{multicols}{2}
    \begin{flushleft}
      \fontsize{30pt}{25pt}
      \fontspec[Path = fonts/ZillaSlab/]{ZillaSlab-Light}
      {{ #1 }\\{ #2 }}
      \columnbreak\\
    \end{flushleft}
    \begin{flushright}
      { #3 }
    \end{flushright}
  \end{multicols}
  \vspace{-8pt}
}

\newcommand{\subheading}[2]{
  {\subsection{#1}
  \hfill{#2}}\\
  \vspace{2pt}
}

\newcommand{\subsubheading}[2]{
  % \vspace{-2pt}
  {\subsubsection{#1}
  \hfill \small#2} \\
  \vspace{2pt}
}

\newcommand{\descript}[1]{
  {\color{subheadingclr}
  \raggedright\fontspec[Path = fonts/Raleway/]{Raleway-Medium}\fontsize{10pt}{12pt}\selectfont {\scshape#1} \normalfont}
}

\newcommand{\datelocation}[1]{
  {\color{date}\fontsize{10pt}{12pt}\bfseries { #1 } \normalfont\\}
}

% custom environments
\newenvironment{tightemize}{
\vspace{-4pt}
\begin{itemize}
  \itemsep3pt \parskip0pt \parsep0pt}
{\end{itemize}\vspace{-\topsep}}

% Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\namesection{Chandrashekhar}{Tripathi}{+91 (844) 805-2150\\
  \href{mailto:tripathics17@gmail.com}{tripathics17@gmail.com}
  \par
  National Institute of Technology\\
  Arunachal Pradesh (IN)}

\centering{
  LinkedIn://\href{https://linkedin.com/in/tripathics}{\textbf{tripathics}} | 
  \href{https://tripathics.github.io}{tripathics.github.io} | 
  GitHub://\href{https://github.com/tripathics}{\textbf{tripathics} }
}
\noindent\makebox[\linewidth]{\color{light}\rule{\paperwidth}{0.2pt}}
\vspace{-5pt}

\begin{multicols}{2}
  \begin{flushleft}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    \section{Education}    
    \subsection{NIT Arunachal Pradesh}
    \subsubheading{B. Tech in Computer Science Eng}{Oct 2020-2024}
    Cum. GPA: \textbf{8.63 / 10 (current)}

    \subsection{Govt. Higher Sec. School, Rupa}
    \subsubheading{Higher Secondary, XII (CBSE)}{Grad. Mar 2019}
    Percentage: \textbf{81.6\%}

    \subsubheading{Secondary, X (CBSE)}{Grad. Mar 2017}
    Cum. GPA: \textbf{10 / 10}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % PROJECTS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    \section{Projects}

    \href{https://github.com/tripathics}{View all projects on GitHub}

    \subheading{Atulyam'23 website}{
      \href{https://atulyam23.com}{Website} | 
      \href{https://github.com/tripathics/atulyam-2023}{Source} 
    }
    \begin{tightemize}
      \item Designed and Developed NITAP's \textbf{Atulyam Fest} \href{https://atulyam23.com}{website}, utilizing \textbf{frontend design} skills to create a magazine-style UI/UX. Utilized \textbf{React + Firebase + Framer Motion (for animations)}.
    \end{tightemize}

    \subheading{Technodaya Website}{
      \href{https://technodaya.vercel.app}{Website} | 
      \href{https://github.com/tripathics/technodaya}{Source}
    }
    \begin{tightemize}
      \item Built the \textbf{Technodaya Newsletter} website using \textbf{NextJS + Firebase} which allows members to submit their activities and articles in predefined formats and admins to review and publish, eliminating all paperworks, saving time and effort.
    \end{tightemize}

    \subheading{Airavat}{\href{https://github.com/tripathics/airavat}{Source}}
    \begin{tightemize}
      \item Build a \textbf{full stack} IoT ecosystem for fleet vehicle monitoring and tracking for transport department of NIT Arunachal Pradesh.
      \item Utilized MERN stack for web application and \textbf{Arduino, NodeMCU and GPS NEO-7M } for the tracker device.
    \end{tightemize}

    \subheading{SHIELD Web App}{\href{https://github.com/tripathics}{Source}}
    \begin{tightemize}
      \item Co-developed \textbf{SHIELD}, an IoT-based ecosystem for secure transportation of valuables with \textbf{Team Revolutionists}. 
      \item Created a ReactJs web app with Firebase backend enabling shipment tracking, locking/unlocking, monitoring with alerts for admins.
      \item Awarded \textbf{1\textsuperscript{st} place} in the NVCTI Winter Challenge Hackathon.
    \end{tightemize}

    \columnbreak

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    
    \section{Skills}

    \begin{tightemize}
      \item \textbf{LANGUAGES}:\\
      C/C++, JavsScript, Java, Python, Bash
      \item \textbf{OPERATING SYSTEM}:\\
      Linux (Ubuntu)
      \item \textbf{TOOLS AND TECHNOLOGIES}:\\ 
      NextJS, React, Node.js/Express.js (Basics), Git/GitHub, MongoDB, Firebase
      \item \textbf{OTHERS}:\\      
      Technical writing
    \end{tightemize}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    % EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    
    \section{Experience}

    \subheading{Alumni cell, NITAP}{\descript{Coordinator}}
    \datelocation{Feb 2023 - Present | NIT Arunachal Pradesh}
    \begin{tightemize}
      \item Building an application for the alumni cell to manage alumni data and events. Utilizing \textbf{React, Node.js/Express.js, MySQL} to eliminate the need for manual data entry hereby saving time and effort.
    \end{tightemize}

    \subheading{Indian Oil Corp. Ltd}{\descript{SDE Intern}}
    \datelocation{Dec 2022 - Jan 2023 | Assam, IN}

    \begin{tightemize}
      \item Worked on the development of \textbf{MERN} web applications for tracking vehicles working inside the refinary.
    \end{tightemize}

    \subheading{Technodaya}{\descript{Editor}}
    \datelocation{Sep 2022 - Present | NIT Arunachal Pradesh}
    \begin{tightemize}
      \item Working as an editor and maintainer of the \textbf{Technodaya Newsletter} \href{https://technodaya.vercel.app}{website}.
      \item Built the application for the editorial team using \textbf{NextJS} and \textbf{Firebase} to eliminate the need to manually correct and upload each activities submitted by the members.
    \end{tightemize}

    \subheading{Ekarigari Solutions Pvt. Ltd}{\descript{IoT Intern}}
    {
      \color{date}\fontsize{10pt}{12pt}\bfseries
      Aug 2022 - Sep 2022 | Remote
    }
    \begin{tightemize}
      \item Worked with the business partners building a Smart Home Automation system using \textbf{NodeMCU + Arduino} hereby learning about the \textbf{IoT} ecosystem.
    \end{tightemize}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%50
    % ACHIEVEMENTS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
    \section{Achievements}
    \begin{tabular}{rll}
      2022 & 1st prize & NVCTI winter challenge Hackathon\\
      2022 & 1st prize & NITAP Designathon\\
      2022 & 1st rank, district & CBSE, AISSCE 2019 \\
    \end{tabular}
  \end{flushleft}
\end{multicols}

\end{document}